---
title: "hw04_yeonuk"
output: github_document
---

Package info: I used *tidyverse*, *gapminder*, and *cowplot* (cowplot for plot layout).
```{r echo=FALSE}
suppressPackageStartupMessages(library(tidyverse)) 
suppressPackageStartupMessages(library(dplyr))
suppressPackageStartupMessages(library(gapminder))
suppressPackageStartupMessages(library(cowplot))
```



# Q1. Reshaping

## My choice: Activity #2

### 1.1. Make a table
- Make a tibble with one row per year and columns for life expectancy for two or more countries.
- Use *knitr::kable()* to make this table look pretty in your rendered homework.

```{r}

new_lifeExp <- gapminder %>%
  filter(country %in% c("China", "Korea, Rep.","Japan","Mongolia", "Taiwan")) %>%
  select(country, year, lifeExp) %>% 
  group_by(year) %>% 
  spread(key=country, value=lifeExp)
knitr::kable(new_lifeExp)

```

### 1.2. Make a figure
- Take advantage of this new data shape to scatterplot life expectancy for one country against that of another.

```{r}
P1 <- new_lifeExp %>% ggplot(aes(x = China, y=`Korea, Rep.`, size = year)) + 
  geom_point() + ggtitle("Life Expectancy") + theme_bw()
P2 <- new_lifeExp %>% ggplot(aes(x = China, y=Japan, size = year)) + 
  geom_point() + ggtitle("Life Expectancy") + theme_bw()
P3 <- new_lifeExp %>% ggplot(aes(x = China, y=Mongolia, size = year)) + 
  geom_point() + ggtitle("Life Expectancy") + theme_bw()
P4 <- new_lifeExp %>% ggplot(aes(x = China, y=Taiwan, size = year)) + 
  geom_point() + ggtitle("Life Expectancy") + theme_bw()

plot_grid(P1,P2,P3,P4, ncol = 2, nrow = 2, label_size = 8)
```

##### Reflection
I compared countries in EastAsia. The table column by each country looks useful when we compare time series variables. This table is also useful when making a scatter plot.


# Q2. Join, merge, look up

## My choice: Activity #1
Create a second data frame, complementary to Gapminder

- Complementary variables: languages, G20, OECD
- Countries: "China", "Korea, Rep.","Japan","Mongolia", "Taiwan", "Canada", "Argentina"
- Overlaped variables with gapminder: country, continent

```{r}
# making a data frame
country <- c("China", "Korea, Rep.","Japan","Mongolia", "Taiwan", "Canada", "Argentina")
continent <- c("Asia","Asia","Asia","Asia","Asia","Americas","Americas")
languages <- c("Mandarin","Korean","Japanese","Mandarin","Mandarin", "English", "Spanish")
G20 <- c(1,1,1,0,0,1,1) # 1: in G20, 0: not in G20
OECD <- c(0,1,1,0,0,1,0) # 1: in OECD, 0: not in OECD

complementary <- data.frame(country, continent, languages, G20, OECD)

knitr::kable(complementary)
```


```{r}
# Making a subset of gapminder in order to use join with small data frame
gapminder_Asia2007 <- gapminder %>% 
  filter(continent == "Asia" & year == 2007 & lifeExp >=65) %>%
  select(country, continent, gdpPercap, lifeExp, pop)

knitr::kable(gapminder_Asia2007)

```


### 2.1. Using left join1
```{r}
left <- left_join(complementary, gapminder_Asia2007, by="country")
knitr::kable(left)
```

##### Reflection
Data in *gapminder_Asia2007* get into *complementary*. One problem is there are two continent columns (continent.x, continent.y) in the new dataset.


### 2.2. Using left join2
```{r}
left2 <- left_join(complementary, gapminder_Asia2007, by=c("country", "continent"))
knitr::kable(left2)
```

##### Reflection
Using *continent* as well as *country* for left join can fix the problem of the first table.

### 2.3. Using inner join
```{r}
inner <- inner_join(gapminder_Asia2007, complementary, by="country")
knitr::kable(inner)
```

##### Reflection
You can see there is no data for *Canada* and *Argentina* since I used inner join. The dataset *gapminder_Asia2007* does not include the countries in Americas.

### 2.4. Using anti join
```{r}
anti <- anti_join(complementary, gapminder_Asia2007, by="country")
knitr::kable(anti)
```

##### Reflection
By using anti join, you can find *Canada* and *Argentina*.

### 2.5. Using full join
```{r}
full <- full_join(complementary, gapminder_Asia2007, by=c("country","continent"))
full <- arrange(full, continent)
knitr::kable(full)
```

##### Reflection
Finally, I used full join. You can see the union between the two datasets.