---
title: "hw02_yeonuk: Explore Gapminder and use dplyr"
author: "Yeonuk"
date: "September 26, 2017"
output: github_document

---
### Report my process

>
> I just followed the hw02 instruction from bring data to making figures.  
>
> One problem which I've suffered from is that I do not understand the exact meaning of *class*. Frankly speaking, I am not sure my answer for *class* is correct or not. 
> 
> Using the function *kable* is the most easiest thing although I haven't learn in class. Also the tables modified by this function look tidy. I think it is pretty useful when using markdown.
> 



#### 1. Bring rectangular data in

```{r}
suppressPackageStartupMessages(library(tidyverse)) 
suppressPackageStartupMessages(library(gapminder))
knitr::opts_chunk$set(fig.width=4, fig.height=3)
```


#### 2. Smell test the data

- Is it a data.frame, a matrix, a vector, a list?
    + Answer: **data.frame** (see the below resut)

- What’s its class?
    + Answer: **tbl_df** and **tbl** (see the below resut)

```{r}
str(gapminder)
```

- How many variables/columns?
    + Answer: **6** (see the below resut)
- How many rows/observations?
    + Answer: **1704** (see the below resut)

```{r}
c(ncol(gapminder), nrow(gapminder))
```

- Can you get these facts about “extent” or “size” in more than one way? Can you imagine different functions being useful in different contexts?
    + Answer: I also can use the *str* function to get the numbers of variables and rows (see the first result). As for using different functions, the data types of the *ncol* function and the *nrow* function are *integar* (see the bellow result), so these functions can be used when I need to compute something from the data size (see the bellow example: computing the total number of components).

```{r}
typeof(c(ncol(gapminder), nrow(gapminder)))
(n_total <- ncol(gapminder)*nrow(gapminder)) # 6 * 1704 = 10224
```

- What data type is each variable?
    + Answer: country & continent = *Factor*,   year & pop = *int*,  lifeExp & gdpPercap  = *num* (see the first result) 


#### 3. Explore individual variables

- Pick __at least__ one categorical variable and at least one quantitative variable to explore.
    + I used two categorial variables *year, continent (select Asia only)* and one quantitative variable *lifeExp*
  
- What are possible values (or range, whichever is appropriate) of each variable?
- What values are typical? What's the spread? What's the distribution? Etc., tailored to the variable at hand.
    + Answer: see the bellow summarized table
  
```{r}
STAT <- gapminder %>% group_by(year) %>% filter(continent=="Asia") %>%
                      summarize(MAX = max(lifeExp), MIN = min(lifeExp), 
                      MEAN = mean(lifeExp), SD = sd(lifeExp), 
                      Q1 = quantile(lifeExp,probs=0.25), 
                      Q2 = quantile(lifeExp,probs=0.5),
                      Q3 = quantile(lifeExp,probs=0.75))
knitr::kable(STAT) # life expectation statistic for each year in Asia
```


#### 4. Explore various plot types & Use *filter()*, *select()* and *%>%*

Make a few plots, probably of the same variable you chose to characterize numerically. Try to explore more than one plot type. **Just as an example** of what I mean:

  * A scatterplot of two quantitative variables.

```{r}
p1 <- gapminder %>% filter(year<1980) %>% 
  ggplot(aes(gdpPercap, lifeExp, colour=continent))
p2 <- gapminder %>% filter(year>=1980) %>% 
  ggplot(aes(gdpPercap, lifeExp, colour=continent))
p1+geom_point(alpha=0.3) + scale_x_log10() + geom_smooth(method="lm") # before 1980
p2+geom_point(alpha=0.3) + scale_x_log10() + geom_smooth(method="lm") # after 1980
```

  * A plot of one quantitative variable. Maybe a histogram or densityplot or frequency polygon.
  
```{r}
hist(gapminder$lifeExp)
```


  * A plot of one quantitative variable and one categorical. Maybe boxplots for several continents or countries.
  
```{r, fig.width=10}
p3 <- gapminder %>% filter(continent %in% c("Americas")) %>% 
  group_by(country) %>% filter(median(lifeExp)<65) %>%
  ggplot(aes(country, lifeExp))
p4 <- gapminder %>% filter(continent %in% c("Americas")) %>% 
  group_by(country) %>% filter(median(lifeExp)>=65 & median(lifeExp)<70) %>%
  ggplot(aes(country, lifeExp))
p5 <- gapminder %>% filter(continent %in% c("Americas")) %>% 
  group_by(country) %>% filter(median(lifeExp)>=70) %>%
  ggplot(aes(country, lifeExp))
p3+geom_boxplot() # American countries with low lifeExp
p4+geom_boxplot() # American countries with intermediate lifeExp
p5+geom_boxplot() # American countries with high lifeExp
```


#### 5. But I want to do more!

*For people who want to take things further.*

Evaluate this code and describe the result. Presumably the analyst's intent was to get the data for Rwanda and Afghanistan. Did they succeed? Why or why not? If not, what is the correct way to do this?

> filter(gapminder, country == c("Rwanda", "Afghanistan"))

**The above code is wrong. One country variable cannot be same with the vector. The correct result can come from the code I made:** 

```{r}
a <- filter(gapminder, country %in% c("Rwanda", "Afghanistan"))
knitr::kable(a)

```



