---
title: "hw03: manipulate & explore data (dplyr, ggplot2)"
author: "Yeonuk"
date: "September 28, 2017"
output: github_document
---


##### Packages which I used
```{r}
suppressPackageStartupMessages(library(tidyverse)) 
suppressPackageStartupMessages(library(gapminder))
knitr::opts_chunk$set(fig.width=8, fig.height=5)

```


## Report my process

>
> I worked for **4 tasks** (1st, 2nd, 4th, and 6th tasks). I tried my best to analyze Gapminder data set. All the tasks include figures and tables.   
>
> *Please enjoy the results!!*
> 

## Homework

### Task 1: Get the maximum and minimum of GDP per capita for all continents. 

- See the table and boxplot. 
```{r}
T10 <- gapminder %>% group_by(continent) %>% 
  summarise(MAX = max(gdpPercap),MIN = min(gdpPercap))
T11 <- gapminder %>% filter(gdpPercap %in% T10$MAX) %>% 
  mutate(MAX_info = paste(country, year, sep=", ")) %>% select(MAX_info)
T12 <- gapminder %>% filter(gdpPercap %in% T10$MIN) %>% 
  mutate(MIN_info = paste(country, year, sep=", ")) %>% select(MIN_info)
T1 <- data.frame(T10, T11, T12)

knitr::kable(T1)  

```

```{r}
P1 <- gapminder %>% ggplot(aes(continent, gdpPercap))
P1 + geom_boxplot() +
     geom_text(aes(label=ifelse(gdpPercap %in% c(T1$MAX,T1$MIN), 
                                paste(country,year,sep=", "),''), angle=5))

```


=======
```{r}

```


### Task 2: Look at the spread of GDP per capita within the continents.
```{r}

```

### Task 4: How is life expectancy changing over time on different continents?
```{r}

```

### Task 6: Find countries with interesting stories. Open-ended and, therefore, hard. 
```{r}

```


