---
title: "hw03: manipulate & explore data (dplyr, ggplot2)"
author: "Yeonuk"
date: "September 28, 2017"
output: github_document
---


##### Packages which I used
```{r}
suppressPackageStartupMessages(library(tidyverse)) 
suppressPackageStartupMessages(library(gapminder))

knitr::opts_chunk$set(fig.width=10, fig.height=6)

```


## Report my process

>
> I worked for **4 tasks** (1st, 2nd, 4th, and 6th tasks). I tried my best to analyze Gapminder data set. All the tasks include figures and tables.   
>
> *Please enjoy the results!!*
> 

## Homework

### Task 1: Get the maximum and minimum of GDP per capita for all continents. 

- See the table and boxplot. 

```{r}
# extract max and min of gdpPercap
T10 <- gapminder %>% group_by(continent) %>% 
  summarise(MAX = max(gdpPercap),MIN = min(gdpPercap)) 

# extract country and year which are with max and min of gdpPercap
T11 <- gapminder %>% filter(gdpPercap %in% T10$MAX) %>% 
  mutate(MAX_info = paste(country, year, sep=", ")) %>% select(continent, MAX_info) 
T12 <- gapminder %>% filter(gdpPercap %in% T10$MIN) %>% 
  mutate(MIN_info = paste(country, year, sep=", ")) %>% select(continent, MIN_info)

# rearrange by name of continent (alphabet)
T11 <- arrange(T11, continent) 
T12 <- arrange(T12, continent)

# merge data and make table
T1 <- data.frame(T10, MAX_info=T11$MAX_info, MIN_info=T12$MIN_info)
knitr::kable(T1)  

```

```{r}
#drawing boxplot with texts (country, year) on max and min points
P1 <- gapminder %>% ggplot(aes(continent, gdpPercap))
P1 + geom_boxplot() +
     geom_text(aes(label=ifelse(gdpPercap %in% c(T1$MAX,T1$MIN), 
                                paste(country,year,sep=", "),''), angle=5))

```

### Task 2: Look at the spread of GDP per capita within the continents.
```{r}

```

### Task 4: How is life expectancy changing over time on different continents?
```{r}

```

### Task 6: Find countries with interesting stories. Open-ended and, therefore, hard. 
```{r}

```


