---
title: "hw03: manipulate & explore data (dplyr, ggplot2)"
author: "Yeonuk"
date: "September 28, 2017"
output: github_document
---


##### Packages which I used
```{r}
suppressPackageStartupMessages(library(tidyverse)) 
suppressPackageStartupMessages(library(gapminder))
suppressPackageStartupMessages(library(cowplot))
suppressPackageStartupMessages(library(grid))
suppressPackageStartupMessages(library(gridExtra))
knitr::opts_chunk$set(fig.width=10, fig.height=7)

```


## Report my process

>
> I worked for **4 tasks** (1st, 2nd, 4th, and 6th tasks). I tried my best to analyze Gapminder data set. All the tasks include figures and tables.   
>
> *Please enjoy the results!!*
> 

## Homework

### Task 1: Get the maximum and minimum of GDP per capita for all continents. 

- See the table and boxplot. You can find not only the Max/Min values but also the country and year for the max/min values.

```{r}
# extract max and min of gdpPercap
data10 <- gapminder %>% group_by(continent) %>% 
  summarise(MAX = max(gdpPercap),MIN = min(gdpPercap)) 

# extract country and year which are with max and min of gdpPercap
data11 <- gapminder %>% filter(gdpPercap %in% data10$MAX) %>% 
  mutate(MAX_info = paste(country, year, sep=", ")) %>% 
  select(continent, MAX_info) 
data12 <- gapminder %>% filter(gdpPercap %in% data10$MIN) %>% 
  mutate(MIN_info = paste(country, year, sep=", ")) %>% 
  select(continent, MIN_info)

# rearrange by name of continent (alphabet)
data11 <- arrange(data11, continent) 
data12 <- arrange(data12, continent)

# merge data and make table
Task1 <- data.frame(data10, MAX_info=data11$MAX_info, MIN_info=data12$MIN_info)

rm(data10,data11,data12)
knitr::kable(Task1)

```

```{r}
#drawing boxplot with texts (country, year) on max and min points
Plot1 <- gapminder %>% ggplot(aes(continent, gdpPercap)) +
     geom_boxplot(aes(fill=continent)) +
     geom_text(aes(label=ifelse(gdpPercap %in% c(Task1$MAX,Task1$MIN), 
                                paste(country,year,sep=", \n"),''), angle=5)) +
     scale_y_continuous(limits=c(-10000,120000)) +
     theme_light()+ 
     labs(y="GDP per capita", title="GDP BoxPlot for each continent with max & min info")

Plot1
```

### Task 2: Look at the spread of GDP per capita within the continents.

- See the table and boxplot. 
```{r}
Task2 <- gapminder %>% group_by(continent) %>% 
                      summarize(MAX = max(gdpPercap), MIN = min(gdpPercap), 
                      MEAN = mean(gdpPercap), SD = sd(gdpPercap), 
                      Q1 = quantile(gdpPercap,probs=0.25), 
                      Q2 = quantile(gdpPercap,probs=0.5),
                      Q3 = quantile(gdpPercap,probs=0.75))
knitr::kable(Task2)  
```

```{r, set(fig.height=12)}
Plot2 <- gapminder %>% ggplot(aes(gdpPercap)) 
      
Plot20 <- Plot2 + 
      geom_freqpoly(aes(gdpPercap,..density..,colour=continent), binwidth = 1800) +
      labs(x="GDP per capita", title="GDP histogram for each continent") +theme_bw()
Plot21 <- Plot2 + 
      facet_wrap( ~ continent) + 
      geom_histogram(aes(gdpPercap,..density..), bins =65, colour="blue") +
      labs(x="GDP per capita") +theme_bw()


plot_grid(Plot20, Plot21, ncol = 1, nrow = 2)


```


### Task 4: How is life expectancy changing over time on different continents?
```{r, set(fig.height=30)}
Data4 <- gapminder %>% group_by(continent, year) %>%
  summarise(M = mean(lifeExp), SD = sqrt(var(lifeExp)))

AF <- Data4 %>% filter(continent == "Africa")
AM <- Data4 %>% filter(continent == "Americas")
AS <- Data4 %>% filter(continent == "Asia") 
EU <- Data4 %>% filter(continent == "Europe") 
OC <- Data4 %>% filter(continent == "Oceania") 

Task4 <- cbind(AF,AM,AS,EU,OC)
Task4 <- Task4[-c(1,5,6,9,10,13,14,17,18)]
names(Task4) <- c("year", "AF_mean", "AF_SD", "AM_mean", "AM_SD", 
                  "AS_mean", "AS_SD", "EU_mean", "EU_SD", "OC_mean", "OC_SD")
rm(AF, AM, AS, EU,OC)

knitr::kable(Task4)  

Plot40 <- ggplot(Data4, aes(year,M,colour=continent)) +
    geom_errorbar(aes(ymin=M-SD/2, ymax=M+SD/2), colour="black", width=.5, alpha=0.5) +
    geom_line() +
    geom_point() +
    labs(y="Annual mean for Life Exp with SD") +theme_bw()

Plot41 <- gapminder %>% ggplot(aes(x=year,y=lifeExp, colour=continent)) +
  geom_boxplot(aes(group = year)) +
  facet_grid(continent ~.) +
  labs(y="boxplot for Life Exp") +theme_bw()

plot_grid(Plot40, Plot41, ncol = 1, nrow = 2)
```

### Task 6: Find countries with interesting stories. Open-ended and, therefore, hard. 
```{r}

```


