---
title: "HW10 Data from the Web"
author: "Yeonuk"
date: "December 7, 2017"
output: github_document
---

I worked on *Scrape the web* among the three options.

## Conference Alert.
: 2018 International Academic Conference Alerts
*ConferenceAlert.com is a global platform to list, update & promote your upcoming conferences, events, seminars, webinars & international workshops. With over 100,000 registered subscribers, our users come from diverse academic as well as non-academic backgrounds, including industry experts, seasoned professors & research fellow from various universities. Our platform helps conference/event organizers to exclusively promote their event to the right audience; ensuring best ROI. With us, giving out information about your conference/event is just a few clicks away. Join Conference Alert today!*

- This introduction from the Conference Alert website: https://conferencealert.com/

I tried to get conference information by country. 


### Packages
```{r}
suppressWarnings(suppressMessages(library(tidyverse)))
suppressWarnings(suppressMessages(library(magrittr)))
suppressWarnings(suppressMessages(library(purrr)))
suppressWarnings(suppressMessages(library(glue)))
suppressWarnings(suppressMessages(library(stringr)))
suppressWarnings(suppressMessages(library(rvest)))
suppressWarnings(suppressMessages(library(xml2)))

```


### Get country name
```{r}
url <- "https://conferencealert.com/#"
page <- read_html(url)

page %>%
  html_nodes(css = ".pktin2") %>%
  html_text() 

```

Class of the all countries are *pktin2*.
But.. looks anoying.

### Cut character to get country name
```{r}
con_list <- c(page %>%
               html_nodes(css = ".pktin2") %>%
               html_text() %>%
               strsplit("\t\n   \n")) 

con_list
```

This looks better. 

However, the last countries for each [[n]] are still problematic. See the *Venezuela*

Also, this is a list by continent, but I want to get just a country name data frame.


### Finally get country name.
```{r}
# function for remove "\t\n"
rm_last_chrs <- function(x,n=4){
    num <- nchar(x)
    return(substr(x,1, num-n))
}

for(i in c(1:6)){
  last <- length(con_list[[i]])
  con_list[[i]][last] <- rm_last_chrs(con_list[[i]][last])
}

#change list to data frame (Is it best way??)
use <- c(con_list[[1]],con_list[[2]],con_list[[3]],con_list[[4]],con_list[[5]],con_list[[6]])
tail(df <- data_frame(country = use))

```

You can see the correct name of "Vnezue".

One thing I need to mention is that I don't know the better way to change a list to a data frame or vector than what I did.
If you have some suggestions, please let me know!


### Get link to county conference info.
```{r}

conference_df <- df %>% mutate(Link = glue('https://conferencealert.com/{country}.php'))
head(conference_df)



```

I choose Canada as an example. You can try using different country.


### Get conference links for Canada
```{r}
# Canada conference link
num <- which(conference_df$country=='Canada')
link <- conference_df$Link[num]
  


href <- link %>% read_html() %>%
          html_nodes(css = ".textLeft") %>%
          html_attr("href")

href <- href[!is.na(href)]

head(canada_link <- glue("https://conferencealert.com/{href}"))

```

### Get conference info
```{r}

get_table <- function(link){

df <- data_frame(Title = 
                   link %>% 
                   read_html() %>%
                   html_nodes(".col-md-7") %>%
                   html_nodes("span#eventNameHeader") %>%
                   html_text(),
                Abstract_deadline = 
                   link %>% 
                   read_html() %>%
                   html_nodes(".col-md-7") %>%
                   html_nodes("span#eventDeadline") %>%
                   html_text(),
                Date =
                   link %>% 
                   read_html() %>%
                   html_nodes(".col-md-7") %>%
                   html_nodes("span#eventDate") %>%
                   html_text(),
                Website = 
                   link %>%
                   read_html() %>%
                   html_nodes(".col-md-7") %>%
                   html_nodes("span#eventWebsite") %>%
                   html_text(),
                Organizer = 
                   link %>%
                   read_html() %>%
                   html_nodes(".col-md-7") %>%
                   html_nodes("span#eventOrganiser") %>%
                   html_text(),
                Detail = 
                   link %>% 
                   read_html() %>%
                   html_nodes(".col-md-7") %>%
                   html_nodes("span#eventDescription") %>%
                   html_text()
                   )
return(df)
}



# This loop take long time... so I got only 5 conference data
for (i in c(1:5)){
  if (i==1) {
    canada_conf <- canada_link[i] %>% get_table()
  } else {
    use <- canada_link[i] %>% get_table()
    canada_conf <- rbind(canada_conf,use)
  }
}

knitr::kable(canada_conf)

```



